---
title: "Data 607 Week 7 Assignment"
author: "Coco Donovan"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

## Introduction:

I have created three different files in three different file formats (JSON, HTML
and XML). I chose three different books that focus on the Troubles in Northern
Ireland (a subject that played a large role in my mom's younger years). The goal 
of this assignment is to create three different files in three different file 
formats and display each of them in a data frame. I will attempt to represent the 
data with the same format; however, I will also make a point to recognize when 
the formatting is different as that will inform how I attempt to work with 
different file formats in the future.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Necessary packages

```{r}
library(XML)
library(methods)
library(rjson)
library(dplyr)
```

## XML

```{r}
bookinfo_xml <- xmlToDataFrame('bookinfo.xml')

bookinfo_xml
```

## HTML

```{r}
bookinfo_html <- readHTMLTable('bookinfo.html')

bookinfo_html
```

## JSON

```{r}
bookinfo_json <- fromJSON(file = "bookinfo.json") %>% as.data.frame

bookinfo_json
```


## Are the three data frames identical?

The three data frames are identical in presentation despite the different storage
methods. The challenge with each method seemed to be to find a creative way to 
store the multiple authors. I know that with JSON you can store multiple items 
in an array which is what I had wanted to do, however that method was not working
when I wanted to display my file in a data frame. A similar issue came up with 
my html file (the two authors were stored as one item). Though, the way I stored the two
authors for one book was different as the XML format made it easy to separately 
store authors as individual items. I know I could go back, now that I have the 
files displayed in tables, and separate those authors easily, but this was a 
learning process for different data structures.